A Real-Time Sonar Simulator for Automatic Target Recognition

### 2015-12-17 Simulator/article.tex
la2pdf commit - 2015:12:17	09:57:16	(to.17.des.)
la2pdf commit - 2015:12:17	11:01:02	(to.17.des.)

\begin{figure*}[t]\centering%
\graphicsAI[width=\linewidth]{gfx/scene_coordinate_system.svg}%
\caption{Simulator principle.}\label{simulator_coordinate_system}%
\end{figure*}

@@

One of the major shortcomings of autonomous underwater vehicles (AUVs) is their lack of intelligence. When an AUV equipped with a sonar encounter an interesting object, it would be very beneficial if adapted its behavior to examine the object further. This is challenging as what we deem as interesting is often something that stand out form the background, i.e. it relies on previous knowledge. It would also need to process this information is near real-time to act in an efficient manner.

>>>>

\begin{figure*}[t]\centering%
\graphicsAI[width=\linewidth]{gfx/scene_coordinate_system.svg}%
\caption{Simulator principle. A model of the seafloor and object is loaded into OpenGL. All points in the imaged seafloor region that are visible from the sonar are orthogonally projected onto a view plane. }\label{simulator_coordinate_system}%
\end{figure*}

@@

\IEEEPARstart{O}{ne} of the greatest visions in science is that of artificial intelligence. If we could make machines not only do what we say, but also able to adapt their behaviour to handle the unexpected, the possibilities are perhaps only limited by our imagination. An apparent area of use is devices designed to sense and act without aid, such as autonomous underwater vehicles (AUVs). When an AUV with a sonar imaging system encounter an interesting object, it would be very beneficial if adapted its behavior to examine the object further. This is challenging as it would need to learn in what ways the interesting objects differ from the background, i.e. it relies on previous knowledge. It would also need to process this information is near real-time to act in an efficient manner.
